Direct Entropy Measurement in a Mesoscopic Quantum System

### 2018-02-10 paper/draft.tex
not much changes

% 2/8/2018
% add citations for AFM papers (x2) for degeneracy measurements (vs T) and Beenakker (x1) for Gamma eqn

@@

\paragraph*{Methods} The device was built on a AlGaAs/GaAs heterostructure, hosting a 2D electron gas with density and mobility at \SI{300}{\milli\kelvin} (determined on a separate chip) of \SI{2.42e11}{\per\square\centi\metre} and \SI[per-mode=symbol]{2.56e6}{\square\centi\metre\per\volt\per\second}.   Mesas and NiAuGe ohmic contacts to the 2DEG were defined by standard photolithography techniques, followed by atomic layer deposition of \SI{10}{\nano\metre} $\mathrm{HfO_2}$ to improve the gating stability to the device. Fine gate structures, including the \SI{200}{\nano\metre} diameter quantum dots, were defined by electron beam lithography and deposition of \SI{20}{\nano\metre} Ti/Au. The measurement was carried out in an dilution refrigerator with a base temperature of \SI{14}{\milli\kelvin}.

The conductance of the charge sensor was measured at a DC voltage bias of \SI{200}{\micro\volt}, with the current read out directly or fed into a lockin amplifier.  The temperature of the reservoir could be raised above $T_{MC}$ (to $T_{MC} + \delta T$) using AC or DC current biased through the left (heater) QPC, which was gate-tuned to \SI{20}{\kilo\ohm}. A calibration for $\delta T$ in this mode, using DC current bias $\alpha$ as measured in Fig.~\ref{fig:fig2}b, can be seen in Fig.~\ref{fig:fig2}c. Applying AC current at $f_{Heat} =$ \SI{48.7}{\hertz} yields oscillations in $T_{res}$ at $2f_{heat}$; to leading order $\delta T_{res} \sim P \sim \cos(2 \times (2 \pi f_{heat}) \times t)$. Variations in $g_{sens}$ with $dT$ are captured with a lockin amplifier measuring $g_{sens}$ oscillations at at the second harmonic of $f_{heat}$.

The transition width, $\Theta$, extracted from fits to Eq.~\ref{eqn:g} was found to follow the mixing chamber temperature, $T_{MC}$, to \SI{<100}{\milli\kelvin} (Fig.~\ref{fig:fig2}b). The assumption of thermally broadened transitions greatly simplifies the data analysis, so $T_{MC}$ is fixed at \SI{100}{\milli\kelvin} for most of this work, using Joule heating to raise $T_{res}$ up to \SI{250}{\milli\kelvin}. Measurements of $\Delta S$ are made at $\delta T_{res} = $ \SI{60}{\milli\kelvin} such that no orbital levels above the ground state were excited.

>>>>

% 2/9/2018
% add citations for AFM papers (x2) for degeneracy measurements (vs T) and Beenakker (x1) for Gamma eqn

@@

%\paragraph*{Methods} The device was built on a AlGaAs/GaAs heterostructure, hosting a 2D electron gas with density and mobility at \SI{300}{\milli\kelvin} (determined on a separate chip) of \SI{2.42e11}{\per\square\centi\metre} and \SI[per-mode=symbol]{2.56e6}{\square\centi\metre\per\volt\per\second}.   Mesas and NiAuGe ohmic contacts to the 2DEG were defined by standard photolithography techniques, followed by atomic layer deposition of \SI{10}{\nano\metre} $\mathrm{HfO_2}$ to improve the gating stability to the device. Fine gate structures, including the \SI{200}{\nano\metre} diameter quantum dots, were defined by electron beam lithography and deposition of \SI{20}{\nano\metre} Ti/Au. The measurement was carried out in an dilution refrigerator with a base temperature of \SI{14}{\milli\kelvin}.
%
%The conductance of the charge sensor was measured at a DC voltage bias of \SI{200}{\micro\volt}, with the current read out directly or fed into a lockin amplifier.  The temperature of the reservoir could be raised above $T_{MC}$ (to $T_{MC} + \delta T$) using AC or DC current biased through the left (heater) QPC, which was gate-tuned to \SI{20}{\kilo\ohm}. A calibration for $\delta T$ in this mode, using DC current bias $\alpha$ as measured in Fig.~\ref{fig:fig2}b, can be seen in Fig.~\ref{fig:fig2}c. Applying AC current at $f_{Heat} =$ \SI{48.7}{\hertz} yields oscillations in $T_{res}$ at $2f_{heat}$; to leading order $\delta T_{res} \sim P \sim \cos(2 \times (2 \pi f_{heat}) \times t)$. Variations in $g_{sens}$ with $dT$ are captured with a lockin amplifier measuring $g_{sens}$ oscillations at at the second harmonic of $f_{heat}$.
%
%The transition width, $\Theta$, extracted from fits to Eq.~\ref{eqn:g} was found to follow the mixing chamber temperature, $T_{MC}$, to \SI{<100}{\milli\kelvin} (Fig.~\ref{fig:fig2}b). The assumption of thermally broadened transitions greatly simplifies the data analysis, so $T_{MC}$ is fixed at \SI{100}{\milli\kelvin} for most of this work, using Joule heating to raise $T_{res}$ up to \SI{250}{\milli\kelvin}. Measurements of $\Delta S$ are made at $\delta T_{res} = $ \SI{60}{\milli\kelvin} such that no orbital levels above the ground state were excited.
